### 2018-08-29 case_for_support.tex
Finished partner profiles

  Facilitated by STFC funding via the Newton and GCRF programs (details below) our team of educators and researchers are developing a highly effective data science training programme for Thai students. Within this programme, students work with external research organisations and businesses to gain first-hand experience of using data science to solve real-world problems. To date, this programme has been highly productive, as evidenced by:
  \begin{itemize}
    \item two students presenting peer-reviewed proceedings at three international conferences (one of whom was awarded a ``Best Presentation'' prize);
    \item the publication of five peer-reviewed journal articles or conference proceedings;
    \item successfull collaborations with five external business at the regional level;
    \item keen interest from five national businesses to join our collaboration.
  \end{itemize}
  By building on these sucesses and expanding our external partnerships to a national level, the next phase of our project will establish MFU as a hub for data science research and training within northern Thailand. This will enable future students, businesses and organisations to benefit indefinitely from STFC's present investment.

@@

  \vspace{3mm}
  \noindent
  {\large \bf 1.2 Broadening the impact of our research to local businesses and organisations}

@@

  \begin{itemize}
  \item {\bf Thai AirAsia} is part of the AirAsia group, which is the largest budget airline operating in South East Asia. They are renowned among the air industry for their high levels of aircraft utility (i.e., maximising the time a plane is in the air, and thus generating revenue). A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while they wait for the delivery of spare parts from various warehouses. This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement, and then act upon this when the aircraft was located at an airport with a parts warehouse. AirAsia engineers will share their flight data with our team so that we can adapt the techniques we have developed to identify rare sources in astronomy to better predict rare instances where parts require replacement. To assist with this development, Thai AirAsia have offered to host the students working on the project on a work-experience placement.
  %\item {\bf Thaweeyont} is a chain of bricks-and-mortar stores that specialise in electronic household appliances, furniture, and motorcycles/scooters. They have expanded rapidly over the past decade, and are now looking to expand into more locations. A problem they face when opening new stores is how to predict the types of customer (sex, age, dispoable income, etc.) that are likely to visit the new store, which has knock-on effects on how to stock the new store. Thaweeyont would like a work with small group of students and researchers to investigate how we can adapt the work conducted during the first phase of our GCRF project (see Thanapiriya) to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
  \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand. This region is a popular tourist destination, resulting in a particularly competitive hotel market and corresponding thin margins. Deevana has found that various promotions (e.g., reduced tariffs, free services/experiences, etc.) help boost traffic to their hotels, resulting in fewer empty rooms. At present, however, they use a scatter-gun approach to advertise these promotions, whereas more targeted campaigns based on customer need may deliver better results. Deevana wishes for our students to research how machine learning -- in particular clustering analysis -- could be used to better identify different types of customers and test which promotions are most effective at attracting different customer types. In return, our staff and students will gain experience in a developing technology solutions for one of Thailand's most important economic sectors.
  \item {\bf Biophics} is a Center of Excellence for biomedical and health informatics operating out of the Faculty of Tropical Medicine at Mahidol University, Bangkok. They specialise in the collection and analysis of data relating to the incidence and spread of infectious diseases within Thailand. 
\end{itemize}

  \begin{table}[h]
  \begin{tabular}{p{2.8cm}|p{13.4cm}}
    {\it Partner} & {\it Data handling/analysis needs}\\
    \hline
    \hline
      Thanapiriya plc & A food retail business that wishes to take multiple factors into account to predict optimum stock volumes. This is a categorisation problem (the same type faced with GOTO data) in terms of increase/decrease/no-change of product demand.\\
    \hline
      TAPP Auto & A car sales business seeking to develop a system that can predict the depreciation curve of a given vehicle given multiple input factors. This is a regression and ``missing data'' problem, as commonly found in astronomy data analysis.\\
    \hline
       Pibulsongkram Raj. University & The Academic Resources Office wishes to identify the optimum online resources to meet the needs of different types of users. This can be achieved through ML-based Personalised Service Provision as often used by streaming services.\\
    \hline
      MFU & The Student Office seeks a system to identify the causes of the high student dropout rates in Thai Universities. This is, in part, a categorisation problem, since students can be grouped according to different drop-out factors. \\
    \hline
      M-Store & A retail complex based on MFU's campus seeks to increase footfall by targeting promotions to specific groups. A ML-based clustering analysis will help to identify different categories according to customer information. \\
    \hline
  \end{tabular}
  \caption{\it Our external partners and a brief description of their data handling and analysis needs. }
  \vspace{-5mm}
  \end{table}
  \vspace{3mm}
  \noindent
  {\large \bf 1.3 Description of work to be undertaken}

  \noindent
  Over the twelve month period of the grant, we will (in broadly chronological order; see Gantt Chart):
  \begin{enumerate}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
  \item Have the Thai staff and students currently working on the project visit the UK. The purpose of this visit is provide the students with first-hand experience of presenting to and communicating with their first external partner -- the GOTO collaboration.
  \item Host a networking event in Chiang-Rai, Thailand, where most of the Thai co-Is and external partners are based. All team members and representatives from all external partners will attend. At the event, our team will deliver a series of short presentations to highlight our skills and technology, using GOTO as a case study. Representatives from our external partners will describe their businesses/organisations, the data they hold, and agree with the team their desired outcomes from the project, together with an estimate of their impact.
  \item Each external partner will be assigned at least one primary team member contact (this could be a postgraduate student, in which case a staff researcher will act as a secondary contact). The primary contact will attend on-site fortnightly meetings with the external partner to get to fully understand their data and analysis needs. Such close interaction is vital in order to discriminate between informative vs. non-informative data. After each meeting, the primary contact will report back to the rest of the team to ensure a collaborative effort is maintained. Start researching and testing possible solutions to the external partners' needs.
  \item We will host a second networking event in month 5. By this stage, the team will have a thorough understanding of the data and needs of each external partner and will have researched possible solutions, enabling us to decide on the broad design of what we will deliver to each partner. This design will be discussed and agreed-upon by the external partners during the networking event. 
  \item Our work will focus on delivering the agreed systems by adapting our own and further researching new techniques to meet our partners' needs. As this happens, the purpose of the fortnightly meetings will progressively shift toward feedback sessions, during which the primary contact will demonstrate our systems and allow the end user to suggest improvements. 
  \item At the start of month ten, we will deliver ``Beta versions'' of the systems we have developed. We will train the external partners on how to use the systems and collect any immediate feedback they may have. The systems will then go through a two month-long Beta testing phase by the external partners, who will then report their experience back to the team. During months eleven and twelve we will address any feedback from the Beta testing phase to deliver the final product.
  \item We will host a final networking event to discuss the outcomes, successes/drawbacks, impact-to-date, and future directions of the research and partnerships. This event will coincide with an outreach event to highlight to the public and invited representatives from other businesses/organisations the economic benefits of data science. Part of the goal of this event is to identify future partnerships.
  \end{enumerate}

>>>>

  Facilitated by STFC funding via the Newton and GCRF programs (details below) our team of educators and researchers are developing a highly effective data science training programme for Thai students. Within this programme, students work with external research organisations and businesses to gain first-hand experience of using data science to solve real-world problems. To date, this programme has been highly productive, as evidenced by:
  \begin{itemize}
    \item two students presenting peer-reviewed proceedings at three international conferences (one of whom was awarded a ``Best Presentation'' prize);
    \item the publication of five peer-reviewed journal articles or conference proceedings;
    \item successfull collaborations with five external business at the regional level;
    \item keen interest from four national businesses to work with us in solving their data handling and analysis needs.
  \end{itemize}
  By building on these sucesses and expanding our external partnerships to a national level, the next phase of our project will establish MFU as a hub for data science research and training within northern Thailand. This will enable future students, businesses and organisations to benefit indefinitely from STFC's present investment.

@@

  \vspace{3mm}
  \noindent
  {\large \bf 1.2 Broadening the impact of our research to national businesses and organisations}

@@

  \begin{itemize}
  \item {\bf Thai AirAsia} is part of the AirAsia group, which is the largest budget airline operating in South East Asia. They are renowned among the air industry for their high levels of aircraft utility (i.e., maximising the time a plane is in the air, and thus generating revenue). A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while they wait for the delivery of spare parts from various warehouses. This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement, and then act upon this when the aircraft was located at an airport with a parts warehouse. AirAsia engineers will share their flight data with our team so that we can adapt the techniques we have developed to identify rare sources in astronomy to better predict rare instances where parts require replacement. To assist with this development, Thai AirAsia have offered to host the students working on the project on a work-experience placement.
  \item {\bf Thanapiriya} is a chain of supermarkets spread across various locations in Northern Thailand. They have expanded rapidly over the past decade, and are now looking to expand into more locations. A problem they face when opening new stores is how to predict the types of customer (sex, age, dispoable income, etc.) that are likely to visit the new store, which has knock-on effects on how to stock the new store. Thanapiriya was one of the partners involved in our first GCRF project and would like to continue to work with us. They would like to work with small group of students and researchers to investigate how we can adapt the work conducted during the first phase of our GCRF project to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
  \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand. This region is a popular tourist destination, resulting in a particularly competitive hotel market and corresponding thin margins. Deevana has found that various promotions (e.g., reduced tariffs, free services/experiences, etc.) help boost traffic to their hotels, resulting in fewer empty rooms. At present, however, they use a scatter-gun approach to advertise these promotions, whereas more targeted campaigns based on customer need may deliver better results. Deevana wishes for our students to research how machine learning -- in particular clustering analysis -- could be used to better identify different types of customers and test which promotions are most effective at attracting different customer types. In return, our staff and students will gain experience in a developing technology solutions for one of Thailand's most important economic sectors.
  \item {\bf Biophics} is a Center of Excellence for biomedical and health informatics operating out of the Faculty of Tropical Medicine at Mahidol University, Bangkok. They specialise in the collection and analysis of data relating to the incidence and spread of infectious diseases within Thailand. Biophics would like to work with our students on developing a ML-based algorithm to identify outliers in Tuberculosis (TB) patient records that may help to identify instances of drug resistance. This is a ``rare event'' problem similar to the one we have developed solutions to for analysing GOTO data. Being part of Mahidol University -- Thailand's top-ranked medical school -- Biophics is highly familiar with the anonymisation of patient data to the levels required by Thai law, and no patient data will be shared outside Thailand.
  \item {\bf OpenLandscape} is a provider of cloud computing infrastructure in Thailand. As in western economies, it is predicted that many Thai companies will switch to rented cloud-based infrastructure from in-house computer hardware. In order to grow, OpenLandscape needs to attract more customers, but also be able to predict when those customers will place greatest load on their systems. To help achieve these aims, OpenLandscape would like to work with a group of students to (a) analyse their customer database and usage logs to classify customers according to their usage type, which they will use to target potential customers with bespoke promotions and; (b) analyse the the usage logs of their hardware to predict when those times when there is heaviest load on their systems. Working with OpenLandscape will provide the students involved in the project with experience in one of Thailand's fastest growing industries.
\end{itemize}

  \noindent
  {\large \bf 1.3 Description of work to be undertaken}

  \noindent
  Over the 24-month period of the grant, we will (in broadly chronological order; see Gantt Chart):
  \begin{enumerate}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
  \item Host the first networking event in Chiang-Rai, Thailand (where most of the Thai co-Is are based), attended by all UK and Thai team members and representatives from all our pre-identified external partners. During the event, our team will deliver a series of short (5-10 minute) presentations to highlight our data-led solutions developed during the previous batch of external users, and available expertise within the team. Representatives from our external partners will also be asked give short presentations to describe their business/organisation and what they seek to achieve from the collaboration
  \item Each problem will be assigned a staff researcher as a main contact, who (and other staffs) co-supervise one student group (senior-project group). The role of the primary contact is to have fortnightly meetings with the external partner to present results and receive feedback. After each meeting, the primary contact will report back to the rest of the team to ensure a collaborative effort is maintained. Having identified possible data, the students will visit and work with each external user for 2 weeks to ensure the quality of collected/preprocessed data, with a chance to communicate directly with the user.
  \item By month 4 the team’s work will move to the implementation phase by increasingly focusing on adapting our technology and techniques to the needs of the users. During the fortnightly meetings the teams will demonstrate their solutions and allow the client to suggest improvements.
  \item During month 7, we will host another meeting between UK and Thai team members and representatives from all external partners. This will allow us to revisit the tasks accomplished in the first half, specify the limitations/difficulties identified found during the past six months, and revise the working plan for the rest of the projects. This will include plans for further on-site visits to provide user training, and also the preparation for internships where students can help users to solve more problems.
  \item Our work will focus on delivering the agreed systems by adapting our own and further researching new techniques to meet our partners' needs. As this happens, the purpose of the fortnightly meetings will progressively shift toward feedback sessions, during which the primary contact will demonstrate our systems and allow the end user to suggest improvements. 
  \item At the start of month ten, we will deliver ``Beta versions'' of the systems we have developed. We will train the external partners on how to use the systems and collect any immediate feedback they may have. The systems will then go through a two month-long Beta testing phase by the external partners, who will then report their experience back to the team. During months eleven and twelve we will address any feedback from the Beta testing phase to deliver the final product.
  \item We will host a final networking event to discuss the outcomes, successes/drawbacks, impact-to-date, and future directions of the research and partnerships. This event will coincide with an outreach event to highlight to the public and invited representatives from other businesses/organisations the economic benefits of data science. Part of the goal of this event is to identify future partnerships.
  \end{enumerate}
